\Large \bf Lissy: Experimenting with on-chain order books

### 2021-09-13 LaTeX-LNCS-2022/sections/appendix.tex
changed the L2 diagram, added some texts and a ref to appendix
hooks for improvements
added the cm to appendix

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
\caption{\footnotesize{\textblue{Modify with inbox, sequencer as well}}  \label{fig:lissyl2}}
\end{figure}

@@

>>>>

\begin{figure}[t]
\centering
\includegraphics[width=1\textwidth]{fig/lissyL2.pdf}
\caption{\footnotesize{Overview of \cm on Arbitrum.}  \label{fig:lissyl2}}
\end{figure}

@@

\subsection{Call Markets}
\label{app:cm}
\begin{itemize}
\item The call market first Matches Alice ask order to sell 1 at 10 with Eric's bid order to Buy 3 at 12. The trader happens at the price Alice asks for; 10, and 2 will be given to the miner as a price improvement. This trade fills Alice's order and leaves Eric with a remainder of 2 to buy at 12. 
\item Next, the call market matches Eric's remainder of 2 with the next highest priority ask order in the list which is Bob's order to sell 4 at 10.15. Trade occurs at 10.15 and 1.85 will be given to the miner as a price improvement. This trade fills the remainder of Eric's bid order and leaves Bob with a remainder of 2 to sell at 10.15.
\item The market now matches the next highest bid order in the list, Alex's bid order to buy 1 at 12.15, with the remainder of Bob's ask order to sell 2 at 10.15. Trader occurs at 10.15 and 2 will be given to minder as a price improvement. This trader fills Alex bis order and leaves Bob with a remainder of 1 to sell at 10.15.
\item Next, the market matches Adam's bid order to buy 3 at 13 with the remainder of Bob's ask order to sell 1 at 10.15. Trade occurs at 10.15 and 2.85 will be given to miner as a price improvement. This match fills the Bob order and leaves Adam with a remainder of 2 to buy at 13.
\item The market then matches Sam's ask order to sell 4 at 10.18 with the remainder of Adam's bid order to buy 2 at 13. Trade occurs at 10.18 and 2.82 is given to miner as a price improvement. This trade fills Adam's order and leaves Sam with a remainder of 2 to sell at 10.18 unfilled. 
\end{itemize}
